Cor Compare

### 2022-09-23 graphs_newt_snakes/corcompare.Rmd
I am looking at correlations from different experiments. trying to see if there are big picture differences

library(ggplot2)
library(viridis)
library(colorspace)
library(gridExtra)
library(tidyverse)
require(reshape2)
library(plyr)
library(gridGraphics)
library(grid)
library(knitr)
library("reshape")

@@

- tall map with 5 sections
- tall map with 7 sections
- tall map with 5 sections no heritability
- tall map with 5 sections no interaction

@@

@@

her_cor_tall_file<- read.csv(paste0(filelocation,"/all_cor.txt") , header = TRUE)
her_cor_tall_file$group_rep <- paste0(her_cor_tall_file$snake_mu_rate, "_", her_cor_tall_file$snake_mu_effect_sd,"_",her_cor_tall_file$newt_mu_rate, "_", her_cor_tall_file$newt_mu_effect_sd, "_", her_cor_tall_file$rep)
her_cor_tall_file$group <- paste0(her_cor_tall_file$snake_mu_rate, "_", her_cor_tall_file$snake_mu_effect_sd,"_",her_cor_tall_file$newt_mu_rate, "_", her_cor_tall_file$newt_mu_effect_sd)
her_cor_tall_file$sim=LETTERS[factor(her_cor_tall_file$group)]
her_cor_tall_file$experiment = "C"

inter_cor_tall_file<- read.csv(paste0(filelocation,"/all_cor.txt") , header = TRUE)
inter_cor_tall_file$group_rep <- paste0(inter_cor_tall_file$snake_mu_rate, "_", inter_cor_tall_file$snake_mu_effect_sd,"_",inter_cor_tall_file$newt_mu_rate, "_", inter_cor_tall_file$newt_mu_effect_sd, "_", inter_cor_tall_file$rep)
inter_cor_tall_file$group <- paste0(inter_cor_tall_file$snake_mu_rate, "_", inter_cor_tall_file$snake_mu_effect_sd,"_",inter_cor_tall_file$newt_mu_rate, "_", inter_cor_tall_file$newt_mu_effect_sd)
inter_cor_tall_file$sim=LETTERS[factor(inter_cor_tall_file$group)]
inter_cor_tall_file$experiment = "D"

@@

@@

>>>>

library(ggplot2)
library(viridis)
library(colorspace)
library(gridExtra)
library(tidyverse)
require(reshape2)
library(plyr)
library(gridGraphics)
library(grid)
library(knitr)
library("reshape")
library(dplyr)

@@

- [A] tall map with 5 sections
- [B] tall map with 7 sections
- [C] tall map with 5 sections no heritability
- [D] tall map with 5 sections no interaction

@@

snewt <- read.csv("~/Desktop/snake_newt_real_data.csv", header = TRUE)

@@

her_cor_tall_file<- read.csv("~/Desktop/no_hair/all_cor.txt", header = TRUE)
her_cor_tall_file$group_rep <- paste0(her_cor_tall_file$snake_mu_rate, "_", her_cor_tall_file$snake_mu_effect_sd,"_",her_cor_tall_file$newt_mu_rate, "_", her_cor_tall_file$newt_mu_effect_sd, "_", her_cor_tall_file$rep)
her_cor_tall_file$group <- paste0(her_cor_tall_file$snake_mu_rate, "_", her_cor_tall_file$snake_mu_effect_sd,"_",her_cor_tall_file$newt_mu_rate, "_", her_cor_tall_file$newt_mu_effect_sd)
her_cor_tall_file$sim=LETTERS[factor(her_cor_tall_file$group)]
her_cor_tall_file$experiment = "C"

inter_cor_tall_file<- read.csv("~/Desktop/no_interaction/all_cor.txt", header = TRUE)
inter_cor_tall_file$group_rep <- paste0(inter_cor_tall_file$snake_mu_rate, "_", inter_cor_tall_file$snake_mu_effect_sd,"_",inter_cor_tall_file$newt_mu_rate, "_", inter_cor_tall_file$newt_mu_effect_sd, "_", inter_cor_tall_file$rep)
inter_cor_tall_file$group <- paste0(inter_cor_tall_file$snake_mu_rate, "_", inter_cor_tall_file$snake_mu_effect_sd,"_",inter_cor_tall_file$newt_mu_rate, "_", inter_cor_tall_file$newt_mu_effect_sd)
inter_cor_tall_file$sim=LETTERS[factor(inter_cor_tall_file$group)]
inter_cor_tall_file$experiment = "D"

@@

all_cor_exp$group_exp=paste0(all_cor_exp$group, "_", all_cor_exp$experiment)

@@

## Comparing the Mean

```{r, looking at the mean}

all_cor_exp %>%
  group_by(experiment) %>%
  summarise_at(vars(mean_newt_pheno_By_mean_snake_pheno), list(name = mean), na.rm = TRUE)

all_cor_exp %>%
  group_by(group_exp) %>%
  summarise_at(vars(mean_newt_pheno_By_mean_snake_pheno), list(name = mean), na.rm = TRUE)

I want to compare the different cor values from the simulations, but i also want to look at it simulation by simulation.

I think trials within a simulation experiment (A, B, C, D) should be the same (same mu and mu effect size).

They should also be different between different GA combinations

same GA should be differwent in the different experiments

```{r, wilcoxn test}

wilcox.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno) #AB

wilcox.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #AC

wilcox.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #AD

wilcox.test(GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno,  her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #BC

wilcox.test(GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #BD

wilcox.test(her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #CD

```{r, t test}

#t.test(GA1_cor_tall_file[GA1_cor_tall_file$group == "1e-08_0.005_1e-08_0.005" & GA1_cor_tall_file$rep <= 1,]$mean_newt_pheno_By_mean_snake_pheno,  GA1_cor_tall_file[GA1_cor_tall_file$group == "1e-08_0.005_1e-08_0.005" & GA1_cor_tall_file$rep >= 2,]$mean_newt_pheno_By_mean_snake_pheno) #AA

t.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #AC

t.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #AD

t.test(GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno,  her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #BC

t.test(GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #BD

t.test(her_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  inter_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno) #CD

t.test(GA1_cor_tall_file$mean_newt_pheno_By_mean_snake_pheno,  GA1_cor_tall_7_file$mean_newt_pheno_By_mean_snake_pheno) #AB
